Rotations and Insecticide Resistance initial plots

### 2017-10-11 inst/documents/rotations_notes.Rmd
separate dominance of selection and dominance of cost

@@

~ get Ian to pull changes

>>>>

*11/10/17*

@@

~ check in resistance::fitnessSingleLocus() on separation of dominance of cost & selection. Was probably OK for Levick et al because we didn't have cost in. 
But I think that dominance of cost may be set to 0 which means that the RS experiences no effect of cost.

    a_dom       <- array_named(locusNum=c(1,2), exposure=c('no','lo','hi')) 
    a_dom[1, 'hi'] <- dom1
    a_dom[2, 'hi'] <- dom2

    #exposure 0 'no'
    a_fitloc[ paste0('RS',locusNum), 'no'] <- 1 - (a_dom[locusNum, 'no'] * a_cost[locusNum])
    a_fitloc[ paste0('RR',locusNum), 'no'] <- 1 - a_cost[locusNum]
